Parallel Global Search Algorithm with Local Tuning\\ for Solving Mixed-Integer Global Optimization Problems

### 2021-03-22 2021/Lobachevskii_BarkalovLebedev/Barkalov.tex
replace some figures in black-and-white

\author{\firstname{K.~A.}~\surname{Barkalov}}
\email[E-mail: ]{konstantin.barkalov@itmm.unn.ru}
\affiliation{Lobachevsky State University of Nizhni Novgorod, Gagarin ave. 23, Nizhni Novgorod, 603950 Russia}

\author{\firstname{V.~P.}~\surname{Gergel}}
\email[E-mail: ]{gergel@unn.ru}
\affiliation{Lobachevsky State University of Nizhni Novgorod, Gagarin ave. 23, Nizhni Novgorod, 603950 Russia}

\author{\firstname{I.~G.}~\surname{Lebedev}}
\email[E-mail: ]{ilya.lebedev@itmm.unn.ru}
\affiliation{Lobachevsky State University of Nizhni Novgorod, Gagarin ave. 23, Nizhni Novgorod, 603950 Russia}
%\noaffiliation % If the author does not specify a place of work.

@@

\received{February 20, 2021} % The date of receipt to the editor, i.e. December 06, 2017

\begin{abstract} % You shouldn't use formulas and citations in the abstract.
In this paper, we consider mixed-integer global optimization problems and propose a parallel algorithm for solving problems of this class based on information-statistical approach for solving continuous global optimization problems. Within this algorithm, we suggest using a local tuning scheme based on the assumption that the multiextremality of the discussed problem is weak. 
We also compare the sequential version of the algorithm with other similar methods.
The effectiveness of parallelizing the algorithm has been confirmed by solving a series of mixed-integer global optimization problems on the Lobachevsky supercomputer.
\end{abstract}

@@

In this work, we will use an approach to reducing multidimensional problems to one-dimensional problems based on space-filling curves.
Using mappings of the Peano-Hilbert curve $y(x)$ type, which project the segment $[0,1]$ onto the $N$-dimensional domain (\ref{D}),
we can reduce the multidimensional conditional minimization problem in the domain $D$ to a one-dimensional conditional minimization problem in the segment $[0,1]$
\begin{equation}\label{problem1}
\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}

@@

We shall consider the problem (\ref{problem1}) under the assumption that the functions $g_i(y(x))$ are defined and computable only on the corresponding sets
\[
Q_1=[0,1], \; Q_{i+1}=\left\{x \in Q_i : g_i(y(x)) \leq 0 \right\}, \; 1 \leq i \leq m.
\]

These conditions allow for the classification of points $x \in [0,1]$ in accordance with the number of constraints $\nu(x)$  calculated at this point. The \textit{index} $\nu(x)$ can also be determined using conditions

\begin{equation}\label{nu}
g_i(y(x)) \leq 0, \; 1 \leq i < \nu, \; g_\nu(y(x))>0,
\end{equation}
where the last inequality is excluded from consideration if  $\nu=m+1$.

@@

Determine the maximum value of indices
\begin{equation}\label{Eq:19}
V=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values  
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, j<i\right\}.
\end{equation}
If set $I_\nu$ contains less than two elements or if $\mu_\nu$ from (\ref{Eq:20}) is equal to zero, then use the value $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, calculate values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =  
   \begin{cases}
    -\epsilon_\nu,  \nu < V, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = V,
   \end{cases}
\end{equation}
where $V$ is the maximum index value and the vector
\begin{equation}\label{Eq:22}
\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right),
\end{equation}
with positive components (also referred to as \textit{reserve vector}) is the algorithm parameter.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristics} $R(i)$: 
\begin{eqnarray}\label{R}
&R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),\nonumber \\
&R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,\\
&R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i),\nonumber
\end{eqnarray}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and values $r_\nu>1, 1\leq\nu\leq m+1$, are the algorithm parameters.
\item
Sort characteristics $R(i)$, $1\leq i \leq k+1$, in descending order 	
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and select $p$ intervals with numbers $t_j, 1\leq j \leq p,$ corresponding to the largest characteristics.
\item
Conduct $p$ new trials in parallel at points $x^{k+j}, 1 \leq j \leq p$, calculated by the formulas
\begin{gather*}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-1})=\nu(x_{t_j})=\nu. \\
\end{gather*}

@@

New formulas for calculating the characteristics of search intervals $R'(i)$, which should be used at the 5th step of the algorithm, can be written as
\[
R'(i) = h_i R(i),
\]
where $R(i)$ from (\ref{R}), and a coefficient $h_i$ is calculated  according to the rule
\begin{eqnarray}\label{lR}
& h_i = \left[\frac{\sqrt{(z_i-z_\nu^*)(z_{i-1}-z_\nu^*)}}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})=\nu(x_{i}),\nonumber\\
& h_i = \left[\frac{z_i-z_\nu^*}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})<\nu(x_{i}),\\
& h_i = \left[\frac{z_{i-1}-z_\nu^*}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})>\nu(x_{i}).\nonumber
\end{eqnarray}
Here, the non-negative integer parameter $q$ characterizes the ``degree of locality'' of the search: for $q=0$ the search will have a ``global'' nature, and for $q>1$ -- ``local''. 
Indeed, the coefficient $h_i$ will have the largest value equal to $10^q$ only for those intervals the boundary points of which correspond to the current minimum, i.e. for which the equality $\omega_i = 0$ holds. The specified value of the coefficient $h_i$ will be higher for larger values of the parameter $q$ (which will increase the value of the characteristic of this interval), and will be equal to 1 for $q=0$ (which corresponds to the initial value of the characteristics).

@@

Using the dimensionality reduction scheme by the Peano-Hilbert curve $y(x), x\in [0,1],$ we can associate each minimization problem in $y$ with a one-dimensional minimization problem
\[
 \min{\left\{ g_{m+1}(y(x),u_s):x \in [0,1], \; g_i(y(x),u_s)\leq 0, \; 1 \leq i \leq m\right\}}, s\in\{1,...,S\}.
\]

Now let us consider the mapping
\[
Y(x)=y(x-E(x)), \; x\in[0,S],
\]
which assigns a point on the interval  [0,S] to a point in the domain $D$ ($E(x)$ corresponds to the integer part of the number $x$) and define the functions 
\[
f_i(x) = g_i(Y(x),u_{E(x)+1}), x\in[0,S],
\]
which have jump discontinuities at integer points $x_k = i, 1\leq i \leq S-1$.
The values $z_k = g_\nu(y(x_k))$ from (\ref{trial_result}) at these points will be considered undefined, and the values of the index -- equal to 0, i.e. $\nu(x_k) = 0$ .

Using the above assignments, we can reformulate the original problem as
\begin{equation}\label{problem_is1}
\min \left\{f_{m+1}(x): x \in [0,S], \; f_i(x) \leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}

@@

\bibitem{Boukouvala}
F.~Boukouvala, R.~Misener and C.~A.~Floudas, \textit{Global optimization advances in Mixed-Integer Nonlinear Programming, MINLP, and Constrained Derivative-Free Optimization, CDFO}, European J. Oper. Res. \textbf{252}, 701--727 (2016).

\bibitem{Belotti}
P.~Belotti, J.~Lee, L.~Liberti, F.~Margot and A.~W\"achter, \textit{Branching and bounds tightening techniques for non-convex MINLP}, Optim. Method. Softw. \textbf{24}(4-5), 597--634 (2009).

@@

\bibitem{Deep}
K.~Deep, K.~P.~Singh, M.~L.~Kansal and C.~Mohan, \textit{A real coded genetic algorithm for solving integer and mixed integer optimization problems}, Appl. Math. Comput. \textbf{212}(2), 505--518 (2009).

\bibitem{Schluter}
M.~Schl\"uter, J.~A.~Egea and J.~R.~Banga, \textit{Extended ant colony optimization for non-convex mixed integer nonlinear programming}, Computers and Operations Research \textbf{36}(7), 2217--2229 (2009).

@@

\bibitem{Strongin2013}
R.~G.~Strongin, V.~P.~Gergel, V.~A.~Grishagin and K.~A.~Barkalov, \textit{Parallel computations for global optimization problems} (Moscow State University, Moscow, 2013) [In Russian].

\bibitem{Evtushenko2009} 
Yu.~G.~Evtushenko, V.~U.~Malkova and A.~A.~Stanevichyus, \textit{Parallel global optimization of functions of several variables}, Computational Mathematics and Mathematical Physics \textbf{49}(2), 246--260 (2009).

\bibitem{Zilinskas2011}
R.~Paulavi\v{c}ius, J.~\v{Z}ilinskas and A.~Grothey, \textit{Parallel branch and bound for global optimization with combination of Lipschitz bounds}, Optimization Methods \& Software \textbf{26}(3), 487--498 (2011).

@@

\bibitem{Sergeyev2013}
Ya.~D.~Sergeyev, R.~G.~Strongin and D.~Lera, \textit{Introduction to Global Optimization Exploiting Space-Filling Curves} (Springer Briefs in Optimization, Springer, 2013).

\bibitem{Strongin2020}
R.~Strongin, K.~Barkalov and S.~Bevzuk, \textit{Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints}, Soft Computing \textbf{24}(16), 11853--11865 (2020).

\bibitem{Gergel2020}
V.~Gergel, E.~Kozinov and K.~ Barkalov, \textit{Computationally efficient approach for solving lexicographic multicriteria optimization problems}, Optim. Lett. (2020). DOI: 10.1007/s11590-020-01668-y

\bibitem{Sergeyev2003}
Y.~D.~Sergeyev, P.~Pugliese and D.~Famularo, \textit{Index information algorithm with local tuning for solving multidimensional global optimization problems with multiextremal constraints}, Math. Program. \textbf{96}(3), 489--512 (2003).
2003.

\bibitem{Sergeyev2007}
Y.~D.~Sergeyev, D.~E.~Kvasov and F.~M.~H.~Khalaf, \textit{A one-dimensional local tuning algorithm for solving GO problems with partially defined constraints} Optimization Letters \textbf{1}(1), 85--99 (2007).

\bibitem{Sergeyev2020}
D.~E.~Kvasov, M.~S.~Mukhametzhanov, M.~C.~Nasso and Y.~D.~Sergeyev, \textit{On acceleration of derivative-free univariate Lipschitz global optimization methods}, Lecture Notes in Computer Science \textbf{11974}, 413--421 (2020).

\bibitem{Barkalov2010}
K.~Barkalov, V.~Ryabov, S.~Sidorov, \textit{Parallel scalable algorithms with mixed local-global strategy for global optimization problems}, Lecture Notes in Computer Science \textbf{6083}, 232–240 (2010).

\bibitem{Strongin2018}
R.~G.~Strongin, V.~P.~Gergel, K.~A.~Barkalov and A.~V.~Sysoyev, \textit{Generalized parallel computational schemes for time-consuming global optimization}, Lobachevskii Journal of Mathematics \textbf{39}(4), 576--586 (2018.)

\bibitem{Barkalov2020}
R.~G.~Strongin, V.~P.~Gergel and K.~A.~Barkalov, \textit{Adaptive global optimization based on a block-recursive dimensionality reduction scheme}, Automation and Remote Control \textbf{81}(8), 1475--1485 (2020).

@@

\bibitem{Gaviano}
M.~Gaviano, D.~Lera, D.~E.~Kvasov and Y.~D.~Sergeyev, \textit{Software for generation of classes of test functions with known local and global minima for global optimization}, ACM Trans. Math. Softw. \textbf{29}, 469--480 (2003).

\bibitem{Barkalov2020_1}
K.~Barkalov, I.~Lebedev, M.~Kocheganova, V.~Gergel, \textit{Combining local and global search in a parallel nested optimization scheme}, Communications in Computer and Information Science, \textbf{1263}, 100-112 (2020).

\bibitem{Habashi}
M.~P.~C. Pellissier, W.~G. Habashi, A.~Pueyo. \textit{Optimization via FENSAP-ICE of aircraft hot-air anti-icing systems}, Journal of Aircraft \textbf{48}(1), 265--276 (2011).

%\bibitem{Floudas}
%C.~A.~Floudas and M.~P.~Pardalos, \textit{Recent advances in global optimization} (Princeton University Press, 2016).
%
%\bibitem{Locatelli}
%M.~Locatelli and F.~Schoen, \textit{Global optimization: theory, algorithms and applications} (SIAM, 2013).
%
%
%\bibitem{Pardalos}
%P.~M.~Pardalos, A.~A.~Zhigljavsky and J.~\v{Z}ilinskas \textit{Advances in stochastic and deterministic global optimization} (Springer, 2016).
%
%
%\bibitem{Ciegis}
%R.~\v{C}iegis, D.~Henty, B.~K\r{a}gstr\"om and J.~\v{Z}ilinskas, \textit{Parallel scientific computing and optimization: advances and applications}  (Springer, 2009). 
%
%\bibitem{Luque}
%G.~Luque and E.~Alba, \textit{Parallel genetic algorithms. Theory and real world applications} (Springer-Verlag, Berlin, 2011).
%
%\bibitem{Strongin3}
%R.~G.~Strongin, \textit{Numerical Methods in Multiextremal Problems (Information-Statistical Algorithms)} (Nauka, Moscow, 1978) [In Russian].
%
%\bibitem{Strongin4}
%R.~G.~Strongin and Y.~D.~Sergeyev, \textit{Global multidimensional optimization on parallel computer}, Parallel Computing \textbf{18} (11), 1259--1273 (1992).
%
%\bibitem{Sergeyev4}
%Y.~D.~Sergeyev and V.~A.~Grishagin, \textit{Parallel asynchronous global search and the nested optimization scheme}, J. Comput. Anal. Appl., \textbf{3} (2), 123--145 (2001).
%
%\bibitem{Gergel1}
%V.~P.~Gergel and S.~V.~Sidorov, \textit{A Two-Level Parallel Global Search Algorithm for Solution of Computationally Intensive Multiextremal Optimization Problems}, Lecture Notes in Computer Science \textbf{9251}, 505--515 (2015).
%
%\bibitem{Gergel2}
%V.~Gergel, \textit{An Unified Approach to Use of Coprocessors of Various Types for Solving Global Optimization Problems}, in Proceedings of the Second International Conference on Mathematics and Computers in Sciences and in Industry (MCSI), Sliema, 13--18 (2015).
%
%\bibitem{Barkalov}
%K.~Barkalov, V.~Gergel and I.~Lebedev, \textit{Solving global optimization problems on GPU cluster}, AIP Conference Proceedings \textbf{1738}, 400006 (2016).
%
%\bibitem{Gergel3}
%V.~Gergel and E.~Kozinov, \textit{Efficient methods of multicriterial optimization based on the intensive use of search information}, Springer Proceedings in Mathematics and Statistics \textbf{197}, 27--45 (2017). 
%
%\bibitem{Gergel4}
%V.~Gergel and E.~Kozinov, \textit{Parallel computing for time-consuming multicriterial optimization problems}, Lecture Notes in Computer Science \textbf{10421}, 446--458 (2017).
%
%\bibitem{Gergel5}
%V.~Gergel, V.~Grishagin and A.~Gergel, \textit{Adaptive nested optimization scheme for multidimensional global search}, J. Glob. Optim.  \textbf{66} (1), 35--51 (2016).
%
%\bibitem{Lera}
%D.~Lera, Y.~D.~Sergeyev, \textit{Lipschitz and Holder global optimization using space-filling curves},  Appl. Numer. Math. \textbf{60} (1-2), 115--129 (2010).
%
%\bibitem{Grishagin1}
%V~A.~Grishagin. \textit{On convergence conditions for a class of global search algorithms}, in Proceedings of the 3-rd All-Union seminar ``Numerical methods of nonlinear programming'', Kharkov, 82--84 (1979) [In Russian].
%
%\bibitem{Grishagin2}
%V.~A.~Grishagin, Y.~D.~Sergeyev and R.~G.~Strongin, \textit{Parallel characteristic algorithms for solving problems of global optimization}, J. Glob. Optim. \textbf{10} (2), 185--206 (1997).
%
%\bibitem{Strongin5}
%R.~G.~Strongin, \textit{Algorithms for Multi-extremal Mathematical Programming Problems Employing the Set of Joint Space-filling Curves}, J. Glob. Optim. \textbf{2} (4), 357--378 (1992).
%
%\bibitem{Sysoyev}
%A.~Sysoyev, K.~Barkalov, V.~Sovrasov, I.~Lebedev and V.~Gergel, \textit{Globalizer -- A parallel software system for solving global optimization problems}, Lecture Notes in Computer Science \textbf{10421}, 492--499 (2017). 
%
%\bibitem{Sergeyev7}
%Y.~D.~Sergeyev and V.~A.~Grishagin, \textit{Parallel Asynchronous Global Search and the Nested Optimization Scheme}, J. Comput. Anal. Appl. \textbf{3} (2), 123--145 (2001).
%
%\bibitem{Modorskii}
%V.~Y.~Modorskii, D.~F.~Gaynutdinova, V.~P.~Gergel and K.~A.~Barkalov, \textit{Optimization in design of scientific products for purposes of cavitation problems}, AIP Conference Proceedings \textbf{1738}, 400013 (2016).
%
%\bibitem{Gergel6}
%V.~P.~Gergel, M.~I.~Kuzmin, N.~A.~Solovyov and V.~A.~Grishagin, \textit{Recognition of surface defects of cold-rolling sheets based on method of localities}, International Review of Automatic Control \textbf{8} (1), 51--55 (2015).

>>>>

\author{\firstname{K.~A.}~\surname{Barkalov}}
\email[E-mail: ]{konstantin.barkalov@itmm.unn.ru}
\affiliation{Lobachevskii State University of Nizhni Novgorod,
Gagarin ave. 23, Nizhni Novgorod, 603950 Russia}

\author{\firstname{V.~P.}~\surname{Gergel}}
\email[E-mail: ]{gergel@unn.ru} \affiliation{Lobachevskii State
University of Nizhni Novgorod, Gagarin ave. 23, Nizhni Novgorod,
603950 Russia}

\author{\firstname{I.~G.}~\surname{Lebedev}}
\email[E-mail: ]{ilya.lebedev@itmm.unn.ru} \affiliation{Lobachevskii
State University of Nizhni Novgorod, Gagarin ave. 23, Nizhni
Novgorod, 603950 Russia}
%\noaffiliation % If the author does not specify a place of work.

@@

\received{February 20, 2021;  revised March 02, 2021; accepted March
22, 2021}

\begin{abstract} % You shouldn't use formulas and citations in the abstract.
In this paper, we consider mixed-integer global optimization
problems and propose a parallel algorithm for solving problems of
this class based on information-statistical approach for solving
continuous global optimization problems. Within this algorithm, we
suggest using a local tuning scheme based on the assumption that the
multiextremality of the discussed problem is weak. We also compare
the sequential version of the algorithm with other similar methods.
The effectiveness of parallelizing the algorithm has been confirmed
by solving a series of mixed-integer global optimization problems on
the Lobachevskii supercomputer.
\end{abstract}

@@

In this work, we will use an approach to reducing multidimensional
problems to one-dimensional problems based on space-filling curves.
Using mappings of the Peano--Hilbert curve $y(x)$ type, which
project the segment $[0,1]$ onto the $N$-dimensional domain
(\ref{D}), we can reduce the multidimensional conditional
minimization problem in the domain $D$ to a one-dimensional
conditional minimization problem in the segment $[0,1]$
\begin{equation}\label{problem1}
\varphi(y(x^\ast))=\min \left\{\varphi(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}

@@

We shall consider the problem (\ref{problem1}) under the assumption that the functions $g_i(y(x))$ are defined and computable only on the corresponding sets
\[
Q_1=[0,1], \; Q_{i+1}=\left\{x \in Q_i : g_i(y(x)) \leq 0 \right\}, \; 1 \leq i \leq m.
\]
These conditions allow for the classification of points $x \in
[0,1]$ in accordance with the number of constraints $\nu(x)$
calculated at this point. The \textit{index} $\nu(x)$ can also be
determined using conditions
\begin{equation}\label{nu}
g_i(y(x)) \leq 0, \; 1 \leq i < \nu, \; g_\nu(y(x))>0,
\end{equation}
where the last inequality is excluded from consideration if  $\nu=m+1$.

@@

Determine the maximum value of indices
\begin{equation}\label{Eq:19}
V=\max \left\{\nu = \nu(x_i), \ 1\leq i \leq k\right\}.
\end{equation}
\item
For all values of $\nu, \ 1\leq \nu \leq m+1$, calculate the values
\begin{equation}\label{Eq:20}
\mu_\nu = \max \left\{ \frac{\left|z_i-z_j\right|}{\left(x_i-x_j\right)^{1/N}} : i,j \in I_\nu, j<i\right\}.
\end{equation}
If set $I_\nu$ contains less than two elements or if $\mu_\nu$ from (\ref{Eq:20}) is equal to zero, then use the value $\mu_\nu=1$.
\item
For all non-empty sets $I_\nu$, $1 \leq \nu \leq m+1$, calculate values
\begin{equation}\label{Eq:21}
  z^\ast_\nu =
   \begin{cases}
    -\epsilon_\nu,  \nu < V, \\
    \min{\left\{g_\nu(x_i):i\in I_\nu\right\}}, \nu = V,
   \end{cases}
\end{equation}
where $V$ is the maximum index value and the vector
\begin{equation}\label{Eq:22}
\epsilon _R=\left(\epsilon_1,...,\epsilon_m\right),
\end{equation}
with positive components (also referred to as \textit{reserve vector}) is the algorithm parameter.
\item
For each interval $(x_{i-1},x_i)$,$1 \leq i \leq k+1$, calculate the \textit{characteristics} $R(i)$:
\begin{eqnarray}\label{R}
&R(i)=\Delta_i+ \frac{(z_i-z_{i-1})^2}{(r_\nu\mu_\nu)^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu=\nu(x_{i-1})=\nu(x_i),\nonumber \\
&R(i)= 2\Delta_i-4\frac{z_i-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu(x_{i-1})<\nu(x_i)=\nu,\\
&R(i)= 2\Delta_i-4\frac{z_{i-1}-z^\ast_\nu}{r_\nu\mu_\nu},\;\; \nu = \nu(x_{i-1})>\nu(x_i),\nonumber
\end{eqnarray}
where $\Delta_i=(x_i-x_{i-1})^{1/N}$, and values $r_\nu>1, 1\leq\nu\leq m+1$, are the algorithm parameters.
\item
Sort characteristics $R(i)$, $1\leq i \leq k+1$, in descending order
\begin{equation}\label{Eq:23}
R(t_1)\geq R(t_2)\geq ... \geq R(t_{k})\geq R(t_{k+1})
\end{equation}
and select $p$ intervals with numbers $t_j, 1\leq j \leq p,$ corresponding to the largest characteristics.
\item
Conduct $p$ new trials in parallel at points $x^{k+j}, 1 \leq j \leq p$, calculated by the formulas
\begin{gather*}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}, \; \nu(x_{t_j-1})\neq \nu(x_{t_j}), \\
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}- \frac{\mathrm{sign}(z_{t_j}-z_{t_j-1})}{2r_\nu}\left[\frac{\left|z_{t_j}-z_{t_j-1}\right|}{\mu_\nu}\right]^N, \; \nu(x_{t_j-1})=\nu(x_{t_j})=\nu. \\
\end{gather*}
\end{enumerate}

@@

New formulas for calculating the characteristics of search intervals $R'(i)$, which should be used at the 5th step of the algorithm, can be written as
$
R'(i) = h_i R(i),
$
where $R(i)$ from (\ref{R}), and a coefficient $h_i$ is calculated  according to the rule
\begin{eqnarray}\label{lR}
& h_i = \left[\frac{\sqrt{(z_i-z_\nu^*)(z_{i-1}-z_\nu^*)}}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})=\nu(x_{i}),\nonumber\\
& h_i = \left[\frac{z_i-z_\nu^*}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})<\nu(x_{i}),\\
& h_i = \left[\frac{z_{i-1}-z_\nu^*}{\mu_\nu}+10^{-q}\right]^{-1}, \; \nu(x_{i-1})>\nu(x_{i}).\nonumber
\end{eqnarray}
Here, the non-negative integer parameter $q$ characterizes the ``degree of locality'' of the search: for $q=0$ the search will have a ``global'' nature, and for $q>1$ -- ``local''.
Indeed, the coefficient $h_i$ will have the largest value equal to $10^q$ only for those intervals the boundary points of which correspond to the current minimum, i.e. for which the equality $\omega_i = 0$ holds. The specified value of the coefficient $h_i$ will be higher for larger values of the parameter $q$ (which will increase the value of the characteristic of this interval), and will be equal to 1 for $q=0$ (which corresponds to the initial value of the characteristics).

@@

Using the dimensionality reduction scheme by the Peano--Hilbert
curve $y(x), x\in [0,1],$ we can associate each minimization problem
in $y$ with a one-dimensional minimization problem
\[
 \min{\left\{ g_{m+1}(y(x),u_s):x \in [0,1], \; g_i(y(x),u_s)\leq 0, \; 1 \leq i \leq m\right\}}, s\in\{1,...,S\}.
\]

Now let us consider the mapping
\[
Y(x)=y(x-E(x)), \; x\in[0,S],
\]
which assigns a point on the interval  [0,S] to a point in the domain $D$ ($E(x)$ corresponds to the integer part of the number $x$) and define the functions
\[
f_i(x) = g_i(Y(x),u_{E(x)+1}), x\in[0,S],
\]
which have jump discontinuities at integer points $x_k = i, 1\leq i
\leq S-1$. The values $z_k = g_\nu(y(x_k))$ from
(\ref{trial_result}) at these points will be considered undefined,
and the values of the index -- equal to 0, i.e. $\nu(x_k) = 0$ .
Using the above assignments, we can reformulate the original problem
as
\begin{equation}\label{problem_is1}
\min \left\{f_{m+1}(x): x \in [0,S], \; f_i(x) \leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}

@@

\bibitem{Boukouvala}
F.~Boukouvala, R.~Misener, and C.~A.~Floudas, \textit{Global
optimization advances in Mixed-Integer Nonlinear Programming, MINLP,
and Constrained Derivative-Free Optimization, CDFO}, European J.
Oper. Res. \textbf{252}, 701--727 (2016).

\bibitem{Belotti}
P.~Belotti, J.~Lee, L.~Liberti, F.~Margot, and A.~W\"achter,
\textit{Branching and bounds tightening techniques for non-convex
MINLP}, Optim. Method. Softw. \textbf{24}(4-5), 597--634 (2009).

@@

\bibitem{Deep}
K.~Deep, K.~P.~Singh, M.~L.~Kansal, and C.~Mohan, \textit{A real
coded genetic algorithm for solving integer and mixed integer
optimization problems}, Appl. Math. Comput. \textbf{212}(2),
505--518 (2009).

\bibitem{Schluter}
M.~Schl\"uter, J.~A.~Egea, and J.~R.~Banga, \textit{Extended ant
colony optimization for non-convex mixed integer nonlinear
programming}, Computers and Operations Research \textbf{36}(7),
2217--2229 (2009).

@@

\bibitem{Strongin2013}
R.~G.~Strongin, V.~P.~Gergel, V.~A.~Grishagin, and K.~A.~Barkalov,
\textit{Parallel computations for global optimization problems}
(Moscow State University, Moscow, 2013) [In Russian].

\bibitem{Evtushenko2009}
Yu.~G.~Evtushenko, V.~U.~Malkova, and A.~A.~Stanevichyus,
\textit{Parallel global optimization of functions of several
variables}, Computational Mathematics and Mathematical Physics
\textbf{49}(2), 246--260 (2009).

\bibitem{Zilinskas2011}
R.~Paulavi\v{c}ius, J.~\v{Z}ilinskas, and A.~Grothey,
\textit{Parallel branch and bound for global optimization with
combination of Lipschitz bounds}, Optimization Methods \& Software
\textbf{26}(3), 487--498 (2011).

@@

\bibitem{Sergeyev2013}
Ya.~D.~Sergeyev, R.~G.~Strongin, and D.~Lera, \textit{Introduction
to Global Optimization Exploiting Space-Filling Curves} (Springer
Briefs in Optimization, Springer, 2013).

\bibitem{Strongin2020}
R.~Strongin, K.~Barkalov, and S.~Bevzuk, \textit{Global optimization
method with dual Lipschitz constant estimates for problems with
non-convex constraints}, Soft Computing \textbf{24}(16),
11853--11865 (2020).

\bibitem{Gergel2020}
V.~Gergel, E.~Kozinov, and K.~ Barkalov, \textit{Computationally
efficient approach for solving lexicographic multicriteria
optimization problems}, Optim. Lett. (2020). DOI:
10.1007/s11590-020-01668-y

\bibitem{Sergeyev2003}
Y.~D.~Sergeyev, P.~Pugliese, and D.~Famularo, \textit{Index
information algorithm with local tuning for solving multidimensional
global optimization problems with multiextremal constraints}, Math.
Program. \textbf{96}(3), 489--512 (2003). 2003.

\bibitem{Sergeyev2007}
Y.~D.~Sergeyev, D.~E.~Kvasov, and F.~M.~H.~Khalaf, \textit{A
one-dimensional local tuning algorithm for solving GO problems with
partially defined constraints} Optimization Letters \textbf{1}(1),
85--99 (2007).

\bibitem{Sergeyev2020}
D.~E.~Kvasov, M.~S.~Mukhametzhanov, M.~C.~Nasso, and Y.~D.~Sergeyev,
\textit{On acceleration of derivative-free univariate Lipschitz
global optimization methods}, Lecture Notes in Computer Science
\textbf{11974}, 413--421 (2020).

\bibitem{Barkalov2010}
K.~Barkalov, V.~Ryabov, and S.~Sidorov, \textit{Parallel scalable
algorithms with mixed local-global strategy for global optimization
problems}, Lecture Notes in Computer Science \textbf{6083}, 232--240
(2010).

\bibitem{Strongin2018}
R.~G.~Strongin, V.~P.~Gergel, K.~A.~Barkalov, and A.~V.~Sysoyev,
\textit{Generalized parallel computational schemes for
time-consuming global optimization}, Lobachevskii Journal of
Mathematics \textbf{39}(4), 576--586 (2018.)

\bibitem{Barkalov2020}
R.~G.~Strongin, V.~P.~Gergel, and K.~A.~Barkalov, \textit{Adaptive
global optimization based on a block-recursive dimensionality
reduction scheme}, Automation and Remote Control \textbf{81}(8),
1475--1485 (2020).

@@

\bibitem{Gaviano}
M.~Gaviano, D.~Lera, D.~E.~Kvasov, and Y.~D.~Sergeyev,
\textit{Software for generation of classes of test functions with
known local and global minima for global optimization}, ACM Trans.
Math. Softw. \textbf{29}, 469--480 (2003).

\bibitem{Barkalov2020_1}
K.~Barkalov, I.~Lebedev, M.~Kocheganova, and V.~Gergel,
\textit{Combining local and global search in a parallel nested
optimization scheme}, Communications in Computer and Information
Science \textbf{1263}, 100--112 (2020).

\bibitem{Habashi}
M.~P.~C. Pellissier, W.~G. Habashi, and A.~Pueyo.
\textit{Optimization via FENSAP-ICE of aircraft hot-air anti-icing
systems}, J. of Aircraft \textbf{48}(1), 265--276 (2011).
